General exp analysis -- 4/18/2018

### 2018-11-02 resistingrhythm/analysis/paper_figures_v3.Rmd
Tweak plot colors

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, color="dodgerblue3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="dodgerblue3") +
  labs(title="f.", y="Kappa", x="Osc. rate (Hz)") +
  theme_classic() + 
  # lims(y=c(0, .01)) +
  theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p5

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.6, color="dodgerblue3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="dodgerblue3") +
  geom_hline(yintercept=0, size=0.2) +
  labs(title="c.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  # lims(y=c(-3, 3)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p6

@@

tmp5 <- rbind(tmp3, tmp4)
tmp5 %>% 
  ggplot(aes(x=osc_mode, y=rate_k - rate_ref, color=osc_mode)) +
  geom_point(size=-1, aes(fill=osc_mode)) +
  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
  labs(title="g.", y=expression(Delta*" rate (Hz)"), x="") +
  theme_classic() +
  geom_hline(yintercept=0, size=0.2) +
  # lims(y=c(-3, 3)) +
  scale_fill_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
  scale_color_manual(values=c("dodgerblue3", "black"), name="Oscillation") +
  stat_compare_means(method="wilcox.test", label="p.signif", 
                     label.x=1.3, size=3, show.legend=FALSE) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme(
    legend.position = c(0.15, 2),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    axis.text.x = element_text(angle = 70, hjust = 1),
    plot.title = element_text(hjust = -1.2, size=18, face="bold")) -> p7

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="dodgerblue3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, color="dodgerblue3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="dodgerblue3") +
  labs(title="f.", y="Kappa", x="Osc. rate (Hz)") +
  theme_classic() + 
  # lims(y=c(0, .15)) +
  theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p5

@@

```{r, fig.width=2.4, fig.height=1.7}
# -
# With H, E
# Var
results218 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(kappa_coord - mse_ref), SD=sd(kappa_coord - mse_ref)) -> tmp1

tmp1 %>% 
ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, levels = c(0.026, 0.028, 0.03, 0.032, 0.034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="a", y="Variance (s)", x="Osc. rate (Hz)") +
  scale_color_manual(
    values=c("paleturquoise3", "paleturquoise4", "black", "indianred4", "indianred1"), 
    guide=FALSE) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p1

@@

tmp2 %>% 
ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, levels = c(0.026, 0.028, 0.03, 0.032, 0.034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="b", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  geom_hline(yintercept=0, size=0.2) +
  scale_color_manual(
    values=c("paleturquoise3", "paleturquoise4", "black", "indianred4", "indianred1"), 
    name="Target [Ca]\n(mmolar)") +
  # lims(y=c(0, .01)) 
  # guides(col = guide_legend(ncol = 2)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = -.34, size=18, face="bold"),
    legend.position = c(1.35, 1.5),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm")) -> p2

# p3 <- textGrob("Homeostatsis")
p3 <- textGrob("Synchrony")
p4 <- textGrob("Excitability")

layout_matrix <- rbind(
  c(6, 6, 6, 6), 
  c(3, 1, 1, 5),
  c(3, 1, 1, 5),
  c(3, 1, 1, 5), 
  c(3, 1, 1, 5), 
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(4, 2, 2, 5))

>>>>

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="darkgoldenrod3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, color="darkgoldenrod3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="darkgoldenrod3") +
  labs(title="f.", y="Kappa", x="Osc. rate (Hz)") +
  theme_classic() + 
  # lims(y=c(0, .01)) +
  theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p5

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=rate_k - rate_ref, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="darkgoldenrod3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.6, color="darkgoldenrod3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="darkgoldenrod3") +
  geom_hline(yintercept=0, size=0.2) +
  labs(title="c.", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  # lims(y=c(-3, 3)) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.4, size=18, face="bold")) -> p6

@@

tmp5 <- rbind(tmp3, tmp4)
tmp5 %>% 
  ggplot(aes(x=osc_mode, y=rate_k - rate_ref, color=osc_mode)) +
  geom_point(size=-1, aes(fill=osc_mode)) +
  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
  labs(title="g.", y=expression(Delta*" rate (Hz)"), x="") +
  theme_classic() +
  geom_hline(yintercept=0, size=0.2) +
  # lims(y=c(-3, 3)) +
  scale_fill_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  stat_compare_means(method="wilcox.test", label="p.signif", 
                     label.x=1.3, size=3, show.legend=FALSE) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme(
    legend.position = c(0.15, 2),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    axis.text.x = element_text(angle = 70, hjust = 1),
    plot.title = element_text(hjust = -1.2, size=18, face="bold")) -> p7

@@

ggplot(data=tmp1, mapping=aes(x=osc_rate, y=kappa_coord, group=osc_rate)) +
  geom_jitter(alpha=0.2, size=0.2, position = position_jitter(width = .05), color="darkgoldenrod3") +
  geom_point(data=tmp2, mapping=aes(x=osc_rate - shift, y=M), size=0.8, color="darkgoldenrod3") +
  geom_errorbar(data=tmp2, mapping=aes(x=osc_rate - shift, ymin=M - SD, ymax=M + SD), 
                width=.15, size=0.2, color="darkgoldenrod3") +
  labs(title="f.", y="Kappa", x="Osc. rate (Hz)") +
  theme_classic() + 
  # lims(y=c(0, .15)) +
  theme(plot.title = element_text(hjust = -.6, size=18, face="bold")) -> p5

@@

```{r, fig.width=2.4, fig.height=1.7}
# -
# With H, E
# Var
results218 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp1

tmp1 %>% 
ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, levels = c(0.026, 0.028, 0.03, 0.032, 0.034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="b", y="Kappa", x="Osc. rate (Hz)") +
  scale_color_manual(
    values=c("plum1", "plum2", "black", "plum3", "plum4"), 
    guide=FALSE) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p1

@@

tmp2 %>% 
ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, levels = c(0.026, 0.028, 0.03, 0.032, 0.034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="a", y=expression(Delta*" rate (Hz)"), x="Osc. rate (Hz)") +
  geom_hline(yintercept=0, size=0.2) +
  scale_color_manual(
    values=c("plum1", "plum2", "black", "plum3", "plum4"), 
    name="Target [Ca]\n(mmolar)") +
  # lims(y=c(0, .01)) 
  # guides(col = guide_legend(ncol = 2)) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = -.5, size=18, face="bold"),
    legend.position = c(1.35, 0.0),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm")) -> p2

p3 <- textGrob("Coordination")
p4 <- textGrob("Excitability")

layout_matrix <- rbind(
  c(6, 6, 6, 6), 
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(3, 1, 1, 5),
  c(3, 1, 1, 5),
  c(3, 1, 1, 5), 
  c(3, 1, 1, 5) 
)
